Investigating social change during cultural contact period using geometric morphometry of pottery shapes from Iron Age northeastern Taiwan

### 2020-01-27 analysis/paper/paper.Rmd
remove unused var.test code

knitr::kable(su_manv_tab,
             caption = "The statistics summary of MANOVA test for the PC scores. `Pr(>F)` is the p-value associated with the F statistic of the effect and test statistic. ")
```

@@

```{r variance-test-PCs}
# we don't use CV because that is not good for measurements with no absolute zero
xx <- 
  pc_plot %>% 
  group_by(pcn, phase) %>% 
  summarise(variance = var(pc))

# statistical test to compare the variances of two samples
pc_plot_tests <- 
  pc_plot %>% 
  group_by_at(vars(-pc)) %>% 
  mutate(i = row_number()) %>% 
  ungroup() %>% 
  mutate(phase = as.character(phase),
         pcn = as.character(pcn)) %>% 
  spread(phase, pc) %>% 
  select(-i) %>% 
  nest_legacy(-pcn) %>% 
  mutate(var_test = purrr::map(data, ~broom::tidy(var.test(.x$`Post-European` ,
                                            .x$`Pre-European`)))) %>% 
  unnest(var_test)
```

>>>>

knitr::kable(su_manv_tab,
             caption = "Summary statistics for the MANOVA test on the PC scores. `Pr(>F)` is the p-value associated with the F statistic of the effect and test statistic. ")
```

@@
